---
title: "Global Offences in the Modern World"
subtitle: "Crime Trends and Statistics"
author: Agata Szymańska 
format: revealjs
theme: moon 

---

## Introduction

Crime and offences remain major global challenges in 2025.

Governments, international organizations and researchers study crime data to:
- improve public safety
- understand social problems
- reduce violence and illegal activity
- develop prevention strategies

Global offences affect economies, communities and everyday life.

---


## What are offences?

An offence is an illegal act that violates the law.

Offences can be divided into several categories:
- Property crimes
- Violent crimes
- Financial crimes
- Cybercrime
- Drug-related offences

Different countries may classify offences differently depending on legal systems.

---

## Property crimes

Property crimes involve stealing or damaging property.

Examples include:
- Theft
- Burglary
- Robbery
- Vehicle theft
- Vandalism

Property crimes are among the most commonly reported offences worldwide.

---

## Violent crimes

Violent crimes involve physical harm or threats against people.

Examples:
- Assault
- Homicide
- Domestic violence
- Kidnapping

These offences often have serious social and psychological consequences.

---

## Cybercrime

Cybercrime continues to grow rapidly in 2025.

Common cyber offences include:
- Identity theft
- Online fraud
- Hacking
- Data breaches
- Financial scams

The increase in internet use and digital banking has created more opportunities for cybercriminals.

---

## Global offence statistics

```{r}
global_data <- data.frame(
  Region = c("Asia", "Africa", "Europe", "North America", "South America"),
  Cases_Millions = c(5.1, 4.1, 3.2, 2.8, 2.3)
)

global_data
```

The table above presents simplified example data showing estimated offence cases by region.

---

## Example data (illustrative)

```{r}
offences <- data.frame(
  region = c("Europe", "Asia", "North America", "South America", "Africa"),
  cases = c(3200000, 5100000, 2800000, 2300000, 4100000)
)

offences
```

---

## Offences by region

```{r}
barplot(
  global_data$Cases_Millions,
  names.arg = global_data$Region,
  main = "Estimated offences by region (millions)",
  ylab = "Cases in millions",
  las = 2
)
```

Asia records the largest number of offences in this example dataset due to its large population.

---

## Key observations

- Asia shows the highest number of cases in this dataset  
- Africa and Europe also have high levels  
- South America shows the lowest  

---

## Types of offences worldwide

```{r}
crime_types <- data.frame(
  Type = c("Theft", "Assault", "Fraud", "Cybercrime", "Drug offences"),
  Cases_Millions = c(7, 5, 3, 2, 1.5)
)

crime_types
```

Theft and assault remain among the most common offences globally.

---

## Important note

These numbers are simplified examples.

Real-world crime data varies by country, reporting systems and year.

---

## Comparison of offence types

```{r}
barplot(
  crime_types$Cases_Millions,
  names.arg = crime_types$Type,
  main = "Global offence categories",
  ylab = "Cases in millions",
  las = 2
)
```

Cybercrime continues to increase every year because of technological development.

---

## Factors influencing crime

Several factors may increase crime rates:
- Poverty
- Unemployment
- Lack of education
- Social inequality
- Political instability

Urbanization and population growth can also affect crime levels.

---

## The role of technology

Technology has both positive and negative effects on crime.

Positive effects:
- Better surveillance systems
- Faster communication
- Digital evidence collection

Negative effects:
- Online scams
- Cyberattacks
- Identity theft

---

## International cooperation

Countries cooperate to fight global crime through:
- Information sharing
- International police organizations
- Cybersecurity partnerships
- Border control systems

Organizations such as INTERPOL support international investigations.

---

## Crime prevention

Governments use different methods to reduce offences:
- Education programs
- Community policing
- Stronger cybersecurity
- Social support systems

Crime prevention is often more effective than punishment alone.

---

## Challenges in crime reporting

Crime statistics are not always fully accurate.

Some offences are:
- unreported
- classified differently
- difficult to investigate

This means real crime levels may be higher than official statistics.

---

## Future trends

Experts predict that:
- cybercrime will continue to grow
- financial fraud will become more advanced 
- digital security will become increasingly important

Artificial intelligence may also influence future criminal activity.

---

## Statistical summary

```{r}
summary(global_data$Cases_Millions)
```

The summary statistics show variation in offence levels between regions. Asia records the highest number of cases, while South America records the lowest value in this example dataset.


## Conclusion

Global offences remain an important issue in modern society.

Key points:
- Crime affects all regions of the world
- Different offence types require different solutions
- Technology changes the nature of crime
- International cooperation is essential

Understanding crime data helps societies develop better prevention strategies.

---

## Thank you


